FinalManuscript_DISCS_UG

### 2019-03-06 parts/09_removed.tex

>>>>

%\subsection{DGK Comparison Protocol}
%The DGK system was primarily developed as part of a comparison protocol, a protocol which allows
%It is known that $E(m)^{v_pv_q} \bmod n = 1$ if and only if $m=0$. This allows

%\subsection{The Benaloh cryptosystem}
%The Benaloh cryptosystem, initially proposed by Josh Benaloh in \cite{benaloh_dense_1994}, allows for the encryption of integers in $\mathbb{Z}_r$ for some odd integer $r$. It relies on the hardness of the \textit{discrete logarithm problem}, and is a generalization of the classic Goldwasser--Micali cryptosystem~\cite{goldwasser_probabilistic_1984}. We present here a corrected version by Fousse, et al. \cite{fousse_benalohs_2010} which corrects an error in the key generation algorithm which prevents accurate decryption in some cases.

%\subsubsection{Benaloh Cryptosystem Description}
%We choose an integer $r$ and two large primes $p$ and $q$ such that the following conditions hold:
%\begin{itemize}
%  \item $r$ divides $(p-1)$;
%  \item $\mathrm{gcd}(r,(p-1)/r)=1$;
%  \item $\mathrm{gcd}(r,q-1)=1$.
%\end{itemize}
%Next, let $n=pq$ and $\phi = (p-1)(q-1)$, and choose $y\in \mathbb{Z}_n^* = \{ x \in \mathbb{Z}_n | \mathrm{gcd}(x,n)=1 \}$ such that the following conditions hold:
%\begin{itemize}
%  \item $y^{\phi/r}\neq 1 \bmod n$;
%  \item For all prime factors $s$ of $r$, $y^{\phi/s}\neq 1 \bmod n$.
%\end{itemize}
%We denote the public key to be $(y,r,n)$ and the private key to be $(p,q)$.

%The encryption function to encrypt a plaintext $m \in \mathbb{Z}_r$ is defined as
%\begin{align*}
%  E(m) = y^m \cdot u^r \mod{n},
%\end{align*}
%where $u$ is a random integer in $\mathbb{Z}_n^*$.

%The decryption function to decrypt a ciphertext $c \in \mathbb{Z}_{n}$ is defined as:
%\begin{align*}
%  D(c) = \log_x{c^{\phi/r}} \mod n
%\end{align*}
%where $x = y^{\phi/r}$ and $\log_x{y} = k$ such that $x^k = y \bmod n$.

%Decryption requires the computation of the discrete logarithm, which can be done using a linear search when $r$ is small. For large values of $r$, the baby-step giant-step algorithm can be used to perform decryption in $O(\sqrt{r})$ time \cite{benaloh_dense_1994}.

%\subsubsection{Homomorphic Properties of the Benaloh Cryptosystem}
%Similar to the Paillier cryptosystem, the Benaloh cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
%For all $m_1,m_2 \in \mathbb{Z}_r$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
%\begin{description}
%  \item[Additive homomorphism]
%  \begin{align*}
%    D(E(m_1)y^{m_2}\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used to add a constant)}\\
%    D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
%  \end{align*}
%  \item[Multiplicative homomorphism]
%  \begin{align*}
%    D(E(m_1)^k\bmod n)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
%  \end{align*}
%\end{description}

%As the multiplicative homomorphism was not presented in the original paper, we provide a short proof here.
%\begin{proof}
%  Let $m \in \mathbb{Z}_r$ and $k\in \mathbb{N}$.
%  We consider $E(m)^k\bmod n = (y^m \cdot u^r \bmod{n})^k\bmod n$.
%  \begin{align*}
%    (y^m \cdot u^r \bmod{n})^k\bmod n
%    &= (y^m \cdot u^r)^k \bmod{n}\\
%    &= (y^m)^k \cdot (u^r)^k \bmod{n}\\
%    &= y^{km} \cdot (u^k)^r \bmod{n}\\
%    &= y^{km} \cdot (u^k \bmod{n})^r \bmod{n}
%  \end{align*}
%  Since $u$ is a random integer in $\mathbb{Z}_n^*$, $\mathrm{gcd}(u,n)=1$.
%  This implies $\mathrm{gcd}(u^k,n)=1$, so $u^k \bmod n$ is a random integer in $\mathbb{Z}_n^*$.
%  Therefore, $y^{km} \cdot (u^k \bmod{n})^r \bmod{n} = E(m)^k\bmod n$ is a valid encryption of the message $km$.
%\end{proof}

% \subsection{Secure Exponentiation and Multiplication Protocols}
% \label{ssec:exponentiationprotocol}
% In order to perform polynomial evaluation, we first present a protocol for privacy-preserving exponentiation to a positive integer power, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}.

% The following protocols apply to both the Paillier and DGK cryptosystems, as they share similar homomorphisms. We first present a secure squaring protocol.

% Suppose Alice encrypts an integer $x$ and sends it so Bob has $E(x)$, and wants to obtain $E(x^2)$ without exposing the value of $x$.
% \begin{itemize}
% 	\item Bob first selects a random integer $r$ and computes $E(x+r)$. Bob can do this since $r$ is a plaintext constant.
% 	\item Bob sends $E(x+r)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
% 	\item Alice squares $x+r$ and encrypts the result. She sends $E((x+r)^2)$ to Bob.
% 	\item Bob computes $E(-2rx + r^2)$. He then computes $E((x+r)^2)E(-2rx + r^2) = E(x^2)$.
% \end{itemize}

% We can use the secure squaring protocol to arrive at a secure multiplication protocol, which then allows for the evaluation of polynomials.
% Suppose Alice encrypts integers $x$ and $y$, and Bob has $E(x), E(y)$ and wants to obtain $E(xy)$.
% \begin{itemize}
% 	\item Bob acquires $E(x^2), E(y^2)$ using the secure squaring protocol.
% 	\item Bob sends $E(x+y)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
% 	\item Alice sends $E((x+y)^2)$ to Bob.
% 	\item Bob then computes
% 	\begin{align*}
% 		E((x+y)^2)E(x^2)^{-1}E(y^2)^{-1} &= E((x+y)^2 - x^2 - y^2)\\
% 		&= E(2xy)
% 	\end{align*}
% 	\item Bob can then recover $E(xy)$ by calcuating for the multiplicative inverse of 2 using the Euclidean algorithm, and calculating $2^{-1}E(xy)$. Such an inverse exists since the modulus is either a prime (in the DGK cryptosystem) or a product of primes greater than 2 (in the Paillier cryptosystem).
% \end{itemize}

\subsection{The Dasgupta--Pal Cryptosystem}
The Dasgupta--Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S. K. Pal \cite{dasgupta_design_2016}, which encrypts integer plaintexts in $\mathbb{Z}_n$ to polynomial ciphertexts. We begin our presentation of the Dasgupta--Pal cryptosystem with the following definition.

Given a message $m \in \mathbb{Z}$, we denote
\begin{align*}
		m_p(x) = a_0 + a_1x + a_2x^2 + \cdots + a_kx^k
\end{align*}
where $a_ka_{k-1}\cdots a_2a_1_0$ is the binary representation of $m$.

In the original scheme presented in \cite{dasgupta_design_2016}, the secret key $S_k$ is set to be a large prime. In Appendix \ref{chap:correction}, we present a case where the Dasgupta--Pal cryptosystem fails and prove that setting the secret key $S_k = 2p$, where $p$ is a large prime, corrects errors in the Dasgupta--Pal cryptosystem.
We now decribe the correct cryptosystem.
\subsubsection{Corrected Dasgupta--Pal Cryptosystem Description}
Let $\ell$ denote the security parameter of the cryptosystem.
Let $S_k = 2p$, where $p$ is a prime number with $\ell - 1$ bits.
Choose a random even integer $z$ of length $\log_2{\ell}$.

Let the secret key be $S_k$, and let the refresh key be $R_k = z \cdot S_k$. The secret key is kept private to the encrypting/decrypting parties, while the refresh key is made publicly available.

The scheme defines the encryption algorithm for a message $m$ as follows:
\begin{align*}
	E(m) = y(x) + S_k\times d(x)
\end{align*}
where
$y(x)$ is a polynomial of degree $n$ such that $m_p(x) \equiv y(x) \bmod S_k$ and $d(x)$ is a randomly chosen polynomial of degree $n$. This encrypts each coefficient of of $m_p(x)$ by adding some multiple of $S_k$ to it. Through this process, each bit of the message is encrypted separately.

Furthermore, the decryption algorithm to recover $m_p(x)$ from a ciphertext polynomial $c(x)$ as
\begin{align*}
	m_p(x) = c(x) \bmod S_k \bmod 2.
\end{align*}
Thus $D(c(x))$ is defined as the integer recovered from the coefficients of the polynomial $c(x) \bmod S_k \bmod 2$.

Dasgupta and Pal note that homomorphic operations on ciphertext introduce noise which may interfere with decryption, due to the potential increase in ciphertext values.
To eliminate noise from a polynomial ciphertext, the following refresh function is used:
\begin{align*}
	R(c(x)) = c(x) \bmod R_k.
\end{align*}

\subsubsection{Homomorphic Properties of the Dasgupta--Pal Cryptosystem}
It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta--Pal cryptosystem. These properties arise since each coefficient in a ciphertext polynomial is essentially an independently encrypted bit of the original message.
\begin{description}
	\item[XOR on ciphertexts]
	A bitwise exclusive or (XOR) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
	\begin{align*}
		D(E(m_1)+E(m_2)) = m_1 \text{ XOR } m_2
	\end{align*}
	\item[AND on ciphertexts]
	Similarly, pair-wise multiplication corresponds to bitwise AND of integer messages.
	\begin{align*}
		D(E(a) \otimes E(b)) = a \text{ AND } b = ab \bmod 2
	\end{align*}
	where $\otimes$ denotes pairwise multiplication,
	\begin{align*}
		\sum_{i=1}^n{a_ix^i} \otimes \sum_{i=1}^n{b_ix^i} = \sum_{i=1}^n{a_ib_ix^i}.
	\end{align*}
\end{description}

Arbitrary computation on data can thus be achived using these bitwise operations. While the Dasgupta--Pal cryptosystem requires significant amounts of memory, as each bit of plaintext is encrypted into an integer, this approach provides a flexible method to perform relatively fast arbitrary computation on encrypted data. Encryption and decryption in the Dasgupta--Pal cryptosystem are accomplished using few arithmetic operations.
